---
title: "Auto3.9"
author: "Rahul Bhat"
date: "6/5/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#######################################################################################
###Exercise 3.9
####This question involves the use of multiple linear regression on the Auto data set.
######################################################################################

```{r}
library(ISLR)
library(corrplot)
library(car)
library(ggplot2)
library(dplyr)
```

####(a). Produce a scatterplot matrix which includes all of the variables in the data set.

```{r}
data(Auto)
pairs(Auto)
```

####(b) Compute the matrix of correlations between the variables using the function cor(). 
####You will need to exclude the name variable, which is qualitative.

```{r}
names(Auto)
correlation <- cor(subset(Auto, select=-name))
correlation
```

####(c) Use the lm() function to perform a multiple linear regression with mpg as the response and all other variables except name as the predictors.

```{r}
lm.fit = lm(mpg~.-name, data = Auto)
summary(lm.fit)
```

####(i). Is there a relationship between the predictors and the response?

```{r}
# Answer: There is such a large F-statistic (2.037105910^{-139}), this provides a strong evidence of relationship between predictor and the response.
```

####(ii). Which predictors appear to have a statistically significant relationship to the response?

```{r}
# Answer: If we look at the p-values associated with each predictor’s t-statistic. We can see that there is a significant relationship with displacement, weight, year and origin.
```

####(iii). What does the coefficient for the year variable suggest?

```{r}
# As we have also mentioned in the second exercise, if the car model is older then the mpg would be higher. If we look at the regression coefficient for year which is "0.7507", it shows that for every one year mpg will keep on increasing by the coefficient. 
```

####(d). Use the plot() function to produce diagnostic plots of the linear regression fit.

```{r}
plot(lm.fit)
plot(predict(lm.fit), rstudent(lm.fit))
# We see from the plot that there is non-linearity with the Residuals vs Fitted plot. From the plot of residuals vs leverage we can see that there is a presence of some outliers which are higher than 2 and lower than -2. There is also one high leverage point which is point 14.
```

####(e). Use the "*" and ":" symbols to fit linear regression models with interaction effects. 

```{r}
lm.fit1 = lm(mpg ~ cylinders * displacement + displacement * weight, data = Auto)
summary(lm.fit1)
# we can see that the interaction between displacement and weight is statistically signifcant, while the interaction between cylinders and displacement is not.
```

####(f) Try a few different transformations of the variables.

```{r}
lm.fit2 = lm(mpg~log(weight)+sqrt(horsepower)+acceleration+I(acceleration^2), data=Auto)
summary(lm.fit2)
plot(lm.fit2)

par(mfrow=c(2,2))
plot(lm.fit2)

plot(predict(lm.fit2), rstudent(lm.fit2))
```