---
title: "Auto2"
author: "Rahul Bhat"
date: "6/3/2017"
output: html_document
---

#####################################################################################
#Exercise 2.9
#####################################################################################

####Load libraries

```{r} 
library(ISLR)
library(corrplot)
library(car)
library(ggplot2)
library(dplyr)
```

####Load Auto dataset

```{r}
data(Auto)
```

####Make sure that the missing values have been removed from the data. So first check the data. 

```{r}
str(Auto)
dim(Auto)
```

####check the list rows of data that have missing values.

```{r}
Auto[!complete.cases(Auto),] 
is.na(Auto) #check missing values
Auto <- na.omit(Auto)  #remove missing values
str(Auto)
```

####(a).Which of the predictors are quantitative, and which are qualitative?

```{r}
summary(Auto)
#Answer - All variables has a numerical structure, hence are quantitative except variable "name" and "origin".
```

####(b). What is the range of each quantitative predictor? You can answer this using the range() function.

```{r}
range(Auto$weight)

range(Auto$acceleration)

range(Auto$year)

range(Auto$cylinders)

range(Auto$mpg)

range(Auto$displacement)

range(Auto$horsepower)
```

####(c) What is the mean and standard deviation of each quantitative predictor?

```{r}

#mean and sd of Auto$acceleration
mean(Auto$weight)
sd(Auto$weight)


#mean and sd of Auto$acceleration
mean(Auto$acceleration)
sd(Auto$acceleration)


#mean and sd of Auto$year
mean(Auto$year)
sd(Auto$year)

#mean and sd of Auto$cylinders
mean(Auto$cylinders)
sd(Auto$cylinders)


#mean and sd of Auto$mpg
mean(Auto$mpg)
sd(Auto$mpg)

# mean and sd of Auto$displacement
mean(Auto$displacement)
sd(Auto$displacement)

# mean and sd of Auto$horsepower
mean(Auto$horsepower)
sd(Auto$horsepower)
```

####(d) Remove 10th to 85 observations and then check mean and sd.

```{r}
Auto2 = Auto[-c(10:85),] #remove 10th to 85 observations
```

####Range after removing 10th and 85th observations

```{r}

#range of Auto2$cylinders
range(Auto2$cylinders)
range(Auto2$mpg)

#range of Auto2$displacement
range(Auto2$displacement)

#range of Auto2$horsepower
range(Auto2$horsepower)

#range of Auto2$weight
range(Auto2$weight)

#range of Auto2$acceleration
range(Auto2$acceleration)

#range of Auto2$year
range(Auto2$year)
```

####Mean and sd after removing 10th to 85th observation.

```{r}
#mean and sd of Auto2$mpg
mean(Auto2$mpg)
sd(Auto2$mpg)


#mean and sd of Auto2$cylinders
mean(Auto2$cylinders)
sd(Auto2$cylinders)


#mean and sd of Aut02$displacement
mean(Auto2$displacement)
sd(Auto2$displacement)


#mean and sd of Auto2$horsepower
mean(Auto2$horsepower)
sd(Auto2$horsepower)

#mean and sd of Auto2$weight
mean(Auto2$weight)
sd(Auto2$weight)


#mean and sd of Auto2$accelertaion
mean(Auto2$acceleration)
sd(Auto2$acceleration)


#mean and sd of Auto2$year
mean(Auto2$year)
sd(Auto2$year)
```

####(e).Investigate the predictors graphically, using scatterplots or other tools of your choice.

```{r}
data("Auto")
str(Auto)
pairs(Auto)
```

####Create some plots highlighting the relationships among the predictors.
```{r}

# There is a correlation between weight and mpg (heavier weight correlated with lower mpg). As the "weight" increases the "mpg"" decreases and vice versa. 
plot(Auto$mpg, Auto$weight) 

# As the number of cylinder increases mpg decreases and vice versa. 
plot(Auto$mpg, Auto$cylinders) 

# Cars will be more efficient over time
plot(Auto$mpg, Auto$year) 

# Cars from origin Japanese(3) have higher mpg than US(1) and European(2) cars.
plot(Auto$mpg, Auto$origin) 
```

```{r}
plot(Auto$weight, Auto$horsepower)
pairs(~ weight + horsepower, Auto)
# As we can see from the plot, there is a positive correlation between weight and horsepower.
```

```{r}
plot(Auto$mpg, Auto$horsepower)
pairs(~ mpg + horsepower, Auto)
# This plot shows that there is a negative correlation between mpg and horsepower.
```

```{r}
pairs(~ mpg + year + horsepower, Auto)
# We can see that from this plot that there is an interesting relationship between Year of manufacture, mpg and horsepower. 
```

####(f) Suppose that we wish to predict gas mileage (mpg) on the basis of the other variables. Do your plots suggest that any of the other variables might be useful in predicting mpg?

```{r}
pairs(Auto)
# Answer: Yes, displacement, weight, horsepower and year, they all are correlated with mpg as we have also mentioned above. Yes, these correlations shows that they would be good predictors to use.
```

